Models of VOR learning in MHC knockout mice

### 2013-02-06 Notes/VORmodel.tex
typo

The evolution of this probability is described by a forgetting matrix, $\frg$:
%
\begin{equation}\label{eq:evolve}
  \diff{\pr(t)}{t} = r\pr(t)\frg,
  \qquad
  \frg = f\pot\M\pot+f\dep\M\dep-\I.
\end{equation}
%
Eventually, this will settle into the equilibrium distribution:
%
\begin{equation}\label{eq:eqprob}
  \eq\frg=0.
\end{equation}
%

@@

The untrained case will be described by $f\pot=f\pot\norm$.
Gain-increase training  will be described by $f\pot=f\pot\inc<f\pot\norm$, and
gain-decrease training  will be described by $f\pot=f\pot\dec<f\pot\norm$. Note that the forgetting matrix \eqref{eq:evolve} and the equilibrium distribution \eqref{eq:eqprob} depend on $f\pot$, which we will indicate with subscripts.

>>>>

The evolution of this probability is described by a forgetting matrix, $\frg$:
%
\begin{equation}\label{eq:evolve}
  \diff{\pr(t)}{t} = r\pr(t)\frg,
  \qquad
  \frg = f\pot\M\pot+f\dep\M\dep-\I,
\end{equation}
where $\I$ is the identity matrix.
%
Eventually, this will settle into the equilibrium distribution:
%
\begin{equation}\label{eq:eqprob}
  \eq\frg=0.
\end{equation}
%

@@

The untrained case will be described by $f\pot=f\pot\norm$.
Gain-increase training  will be described by $f\pot=f\pot\inc<f\pot\norm$, and
gain-decrease training  will be described by $f\pot=f\pot\dec>f\pot\norm$. Note that the forgetting matrix \eqref{eq:evolve} and the equilibrium distribution \eqref{eq:eqprob} depend on $f\pot$, which we will indicate with subscripts.
